%-------------------------
% Resume in Latex
% Author : Timi Akinbaleye
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


% ---------HEADING----------

\begin{center}
    {\Huge \scshape Timi Akinbaleye} \\ \vspace{1pt}
    Toronto, Canada \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 905-965-6789~ \href{mailto:olajonlutimilehin@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{olajonlutimilehin@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/timmyola/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/timmyola}}  ~
    \href{https://github.com/timmyola}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/timmyola}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {York University}{Sep. 2021 -- April 2026}
      {Bachelors of Engineering. Spec. Hons. - Software Engineering}{Toronto, ON}
  \resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Computer Organization
%                 \item Advanced OOP
%                 \item Embedded Systems
%                 \item Software Development
%                 \item Operating Systems
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, C, HTML/CSS, JavaScript, SQL, Swift} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio, Xcode} \\
     \textbf{Technologies/Frameworks}{: Jenkins, GitHub, JUnit, WordPress, TestRail, Selenium, Applium , Charles Proxy, Jira, Confluence} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {theScore}{September 2023 -- Present}
      {Software QA Analyst Co-op}{(remote) Toronto, ON}
\resumeItemListStart
\resumeItem{Conduct cross-platform testing (Android, iOS, Web) for Sports Media and Betting apps to ensure production readiness.}
\resumeItem{Develop comprehensive test plans and cases, employing verification and validation techniques to assess application functionality.}
\resumeItem{Collaborate with cross-functional teams (developers, product managers, designers) to ensure precise product functionality.}
\resumeItem{Manage bug tracking and prioritization using Jira, contributing to an efficient defect life cycle.}
\resumeItem{Contribute to product quality through Bug-bash exercises and ad-hoc testing.}
\resumeItem{Actively participate in daily stand-ups, retrospectives, and knowledge transfer sessions, promoting effective communication and teamwork.}
\resumeItemListEnd

    \resumeSubheading
      {York Univeristy}{March 2023 -- September 2023}
      {DevOps Engineer Intern}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Delivered on-site assistance to address incoming system failure tickets, ensuring minimal downtime. Collaborated closely with end-users to diagnose, troubleshoot, and resolve technical problems. }
        \resumeItem{Worked with IT and Business management to evaluate complex user requests, projects and clarify objectives and functional requirements for new or modified computer programs.}
        \resumeItem{Designing and implementing strategies to improve and automate our environment provisioning, setup and testing processes.}
           \resumeItem{Participated in identifying and resolving technical issues, system failures, and performance bottlenecks in collaboration with the DevOps team.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      % \resumeProjectHeading
      %     {\textbf{Ticket Price Calculator App} $|$ \emph{Java, Android Studio}}{November 2020}
      %     \resumeItemListStart
      %       \resumeItem{Created an Android application using Java and Android Studio to calculate ticket prices for trips to museums in NYC.}
      %       \resumeItem{Processed user inputted information in the back-end of the app to return a subtotal price based on the tickets selected.}
      %       \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
      %     \resumeItemListEnd 
      %     \vspace{-13pt}
      \resumeProjectHeading
          {\href{https://github.com/TC6IDM/Flexx}{\textbf{Flexxx - Java Desktop App} $|$ \emph{Java, SQL, Eclipse, MySQL}}}{April 2023}
    \resumeItemListStart
         \resumeItem{Developed a fitness planner app with advanced algorithms, utilizing JavaFX and databases with SQL, that enables users to create personalized workout plans.}
         \resumeItem{Implemented progress tracking and performance analytics features to help users easily achieve their fitness goals, with a user-friendly GUI.}
         \resumeItem{Conducted extensive user testing and feedback analysis, resulting in improvements to the app's functionality and ensuring a seamless user experience for the users.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
          \resumeProjectHeading
          {\href{https://github.com/timmyola/Message-Me}{\textbf{MessageMe - iOS App} $|$ \emph{Swft, Google Firebase Firestore, Xcode}}}{December 2022}
          \resumeItemListStart
                 \resumeItem{Produced a messaging application containing full functionality of sending and receiving messages.}
            \resumeItem{Implemented Firebase Firestore database to take advantage of a client first SDK and real-time updates allowing to receive and send messages with ease.}
            \resumeItem{Utilized fundamental UI/UX fundamentals to create an aesthetically appealing design. }
            \resumeItem{Executed prominent message application principals to include: profile picture and timestamps.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------INVOLVEMENT---------------
\section{Leadership and Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Lassonde Engineering Society}{April 2022 -- April 2023}{Chief Returning Officer}{York University}
            \resumeItemListStart
                \resumeItem{Ensured fair and diverse candidate election through impartial interviews and equitable access to resources.}
                \resumeItem{Implemented secure voting procedures in collaboration with IT support, resulting in zero reported fraud or irregularities.} 
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
